---
title: "Corona Info Map for the Netherlands"
author: "Zixin"
date: "23/10/2020"
output: html_document
---
<style type = "text/css">

h1,h4{
text-align: center
}
</style>

##### **Leaflet practice**
This report is to practice the package leaflet which is an open-source JavaScript libraries for interactive maps. This map presents three main pieces of information:  

**(1)** Location of Delft, a Netherlands city, which is shown with its own coat of arms  
**(2)** Corona Virus information of Amsterdam in a pop-up window  
**(3)** Up-to-Date reported infection person of the Netherlands in colour-scale  

Presented data is download from https://nlcovid-19-esrinl-content.hub.arcgis.com/datasets/covid-19-actuele-gegevens-rivm-vlakken/data?geometry=-3.561%2C50.825%2C13.127%2C53.192&page=2  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    cache = TRUE)

library(leaflet)
library(dplyr)
library(geojsonio)
```
##### **Reading and processing data**
```{r}
# reading geoJSON data of the Netherlands and pandemic
url <- "https://opendata.arcgis.com/datasets/620c2ab925f64ed5979d251ba7753b7f_0.geojson"
path <- readLines(url)
write(path, file = "data.geojson")
geoData <- geojson_read("data.geojson", what = "sp")
coronaData <- data.frame(townName = geoData$Gemeentenaam, infectionDensity = geoData$Meldingen_100000)

# location of city Delft and Amsterdam
latLonDelft <- c(52.011736, 4.359208)
latLonAms <- c(52.366667,4.9)
```
##### **Generating map**
```{r}
# setting color paletter
pal <- colorNumeric(
  palette = "Oranges",
  domain = coronaData$infectionDensity)

# getting the coat of arms of Delft city
urlIcon = "https://ih0.redbubble.net/image.404393839.2232/flat,1000x1000,075,f.u2.jpg"
DefltIcon <- makeIcon(
  iconUrl = urlIcon,
  iconRetinaUrl = urlIcon,
  iconWidth = 45, iconHeight = 25 )

# the pop-up info of Amsterdam City
amsInfo <- paste(sep = "<br/>",
  "Amsterdam",
  paste("Date: ", Sys.Date(), sep = ''),
  paste(
      "Reported infection per 100,000: ",
      as.character(coronaData$infectionDensity[coronaData$townName == 'Amsterdam']),
      sep = '')
)
# generating map
leaflet(geoData) %>%
    addTiles() %>%
    addPolygons(
        stroke = FALSE, smoothFactor = 0.5, fillOpacity = 0.75,
        fillColor = ~ pal(Meldingen_100000)) %>%
    addMarkers(latLonDelft[2], latLonDelft[1], icon = DefltIcon) %>%
    addLegend(
        "topleft", pal = pal, values = ~ Meldingen_100000,
        title = "Reported per 100,000") %>%
    addPopups(
        latLonAms[2],latLonAms[1],amsInfo,
        options = popupOptions(closeButton = TRUE))
```
    